\ttitle

### 2013-10-03 Chapters/Chapter3/one_class_svm.tex
SVDD

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{./Figures/chapter3/svm_separating_plane_with_margin.png}
  \caption[\gls{svm} and the separating hyperplane]{Illustration of the separating hyperplane of a \gls{svm}. Here $w$ is the normal vector for the separating hyperplane and the distance between the two margins is $\frac{2}{\lVert{w}\rVert}$.}
  \label{fig:svm_hyperplane}
\end{figure}
*** Add wikipedia reference. How to do? http://en.wikipedia.org/wiki/File:Svm_max_sep_hyperplane_with_margin.png ***

@@

\begin{figure}
\centering
  \includegraphics[width=0.8\textwidth]{./Figures/chapter3/svm_kernel_mapping.png}
  \caption[Kernel mapping]{The non-linear boundary in the input space $I$ (left) is transformed to a linear boundary in the feature space $F$ (right) by mapping the data points with the function $\phi$. The kernel trick uses a function $K$ which performs an implicit mapping.}
  \label{fig:kernel_mapping}
\end{figure}
*** Add wikipedia reference. How to do? http://en.wikipedia.org/wiki/File:Kernel_Machine.png ***

@@

\subsection{\acrlong{svdd}}\label{subsec:svdd}
\emph{Explain working of \gls{svdd} by Tax and Duin, \cite{tax2004support}}

>>>>

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{./Figures/chapter3/svm_separating_plane_with_margin.png}
  \caption[\gls{svm} and the separating hyperplane]{Illustration of the separating hyperplane of a \gls{svm}. Here $w$ is the normal vector for the separating hyperplane and the distance between the two margins is $\frac{2}{\lVert{w}\rVert}$. *** Add wikipedia reference. How to do? ***}
  \label{fig:svm_hyperplane}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.8\textwidth]{./Figures/chapter3/svm_kernel_mapping.png}
  \caption[Kernel mapping]{The non-linear boundary in the input space $I$ (left) is transformed to a linear boundary in the feature space $F$ (right) by mapping the data points with the function $\phi$. The kernel trick uses a function $K$ which performs an implicit mapping. *** Add wikipedia reference. How to do? ***}
  \label{fig:kernel_mapping}
\end{figure}

@@

\subsection{\acrlong{svdd}}\label{subsec:svdd}
The method introduced by Tax and Duin \cite{tax2004support}, known as \acrlong{svdd}, takes as spherical instead of planar approach.
The boundary, created in feature space $F$, forms a hypersphere around the (high density region of the) data.
The volumne of this hypersphere is minimized to get the smallest enclosing boundary.
By allowing outliers using slacks variables, in the same manner as classical \gls{svm} and \gls{nu-svm}, a soft margin is constructed.

The constructed hypersphere is characterized by a center $\mathbf{a}$ and a radius $R > 0$ as distance from the center to (any data point that is a \gls{sv} on) the boundary, for which the volume, and thus the radius $R$, will be minimized.

\begin{equation}\label{eq:svdd_objective}
  \operatorname*{min}_{R,\ \mathbf{a} } R^2 + C \sum_{i=1}^n \xi_i
\end{equation}
\begin{equation}
  \begin{multlined}
    \mbox{ subject to: } \\
    \begin{aligned}
      \lVert x_i - \mathbf{a} \rVert ^ 2 \leq & R^2 + \xi_i & \mbox{ for all } i = 1, \dots, n \\
      & \xi_i \geq 0 & \mbox{ for all } i = 1, \dots, n \\
    \end{aligned}
  \end{multlined}
\end{equation}

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth,keepaspectratio]{./Figures/chapter3/nu-vs-svdd.pdf}
  \caption[Difference \gls{nu-svm} and \gls{svdd}]{Graphical representation of the difference between \gls{nu-svm} (left) and \gls{svdd} (right). Note that for the sake of simplicity the kernel functions are not applied.}
  \label{fig:nu-vs-svdd}
\end{figure}
